Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-17 Grassmannian_cells.tex
Added independence of construction of cells to Theorem 4.20

The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge2$, the following hold:
  \begin{enumerate}
    \item For $i\in\{1,\ldots,n\}$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$ and any $J\subsetneq\{i\}^c$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{
           \ar[r] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[d]
          & \ar[r] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[d] \ar_{\tilde\pi_{m,i}^{\{j\}^c}}[dl] 
          & \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[d] \ar_{\tilde\pi_{m+1}^{\{i\}^c}}[dl]\\ 
          \tilde P_{m-1,(i,j)}^{\{j\}}\cong \tilde P_{m,i}^{\{j\}^c}
          & \tilde P_{m,i}^{\{i\}}\cong\tilde P_{m+1}^{\{i\}^c} \ar_(.4){\tilde\pi_{m,i}^{\{j\}^c,\{i\}}}[l] 
          & \tilde P_{m+1}^J \ar_(.4){\tilde\pi_{m+1}^{\{i\}^c,J}}[l]}
      \end{equation}
    \item For an admissible sequence $\ui\in A_1^{(k)}$, $1\le k< m$, and $J\subsetneq\{1,\ldots,n\}$, the restriction of $\tilde\pi_{m+1}^J:\tilde P_{m+1}\to\tilde P_{m+1}^J$ to $\tilde P_{m+1-k,\ui}$ is injective if $J\subsetneq\{i_1\}^c$ and is zero if $i_1\in J$.
    \item For any admissible word $\ui\in A_1^{(k)}$ with $0\le k< m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with~$i_k\in I$ and $i_1\notin J$ if $k\ge1$ or with $J\subsetneq I$ if $k=0$, there exist (unique up to scale) surjective maps~$\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$.
      These satisfy the following relations:
      \begin{itemize}
        \item $\tilde\pi_{m+1}^{\ui,I,J}\circ\tilde\pi_{m+1}^{J,K}=\tilde\pi_{m+1}^{\ui,I,K}$ for $K\subsetneq J$;
          \item $\tilde\pi_{m+1-k,\ui}^{H,I}\circ\tilde\pi_{m+1}^{\ui,I,J}=\tilde\pi_{m+1}^{\ui,H,J}$ for $I\subsetneq H\subsetneq\{1,\ldots,n\}$;
        %\item $\tilde\pi_{m+1}^{\ui,\varnothing,I}\Big|_{\tilde P_{m+1-k,\ui}} =\tilde\pi_{m+1-k,\ui}^I$;
        \item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $0\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
      \end{itemize}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

@@

  The diagrams from (2) stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
  \[\tilde\pi_{m+1}^{\ui,I,J}:=\tilde\pi_{m+1-k,\ui}^{I,\{i_k\}}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_k\}^c,\{i_{k-1}\}}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_2\}^c,\{i_1\}}\circ\tilde\pi_{m+1}^{\{i_1\}^c,J}.\]
  These can be seen to satisfy the desired properties from (4) inductively using Lemma~\ref{le:properties}.5 and the commutativity from (2).
\qed\end{proof}

The next technical results illustrate the need to lift to the universal covering quiver $\widetilde K(n)$.
\begin{lemma}
  \label{le:special subrepresentations}
  Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
  \begin{enumerate}
    \item For $m\ge2$, we have $\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)\cong\CC$.
      Moreover, the kernel of a nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is the following representation 
      \[\tilde P_m(I,j):=
        \begin{cases}
          \bigoplus_{\substack{1\leq k\leq n\\k\neq j}}\tilde P_{m-1,(j,k)}\oplus \bigoplus_{i\in I\setminus\{j\}}\tilde P_{m-2,(j,j,i)} & \text{ if $m\geq 3$;}\\
          \bigoplus_{\substack{1\leq k\leq n\\k\neq j}}\tilde P_{1,(j,k)} & \text{ if $m=2$.}
        \end{cases}\]
    \item For $m\ge3$, any nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is surjective.
  \end{enumerate}
\end{lemma}
\begin{proof}
  The first claim of part (1) follows immediately by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} to Lemma~\ref{le:properties}.3.
  Indeed, this gives
  \[\dim\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})=1.\]

@@

  Since the evaluation map $ev_I$ in equation~\eqref{ses1} is irreducible, any nontrivial map to $\tilde P_{m-1}^{I\setminus\{j\}}$ must factor through $\tilde P_{m-1}$.
  It then follows from Lemma~\ref{le:homdecomposition} that $\tilde P_{m-1,(j,k)}$ is in the kernel of the vertical morphism $\eta$ for $k\ne j$.
  Therefore $\ker\eta$ is the direct sum of these with the kernel of the induced map $\tilde P_{m-1}\to\tilde P_{m-1}^{I\setminus\{j\}}$, that is with $\bigoplus_{i\in I\setminus\{j\}} P_{m-2,i}=\bigoplus_{i\in I\setminus\{j\}} P_{m-2,(j,j,i)}$, and so $\ker\eta=P_m(I,j)$.
  Since $\eta$ and the right hand vertical morphism have the same kernel, this completes the proof of (1).

@@

The following orthogonality property is a primary reason we need to lift to the universal cover of $K(n)$.
As usual, given $\tilde M\in\rep \widetilde{K(n)}$, we write
\[\tilde M^\perp := \{\tilde N\in\rep \widetilde{K(n)}:\Hom(\tilde M,\tilde N)=0=\Ext(\tilde M,\tilde N)\}.\]
\begin{corollary}
  \label{cor:perpendicular}
  Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
  For $m\geq 2$, we have $\tilde P_m(I,j)\in (\tilde P_{m+1}^I)^\perp$.
\end{corollary}
\begin{proof}
  If $m=2$, we have $\Hom\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$ since $\tilde P_2(I,j)$ is a direct sum of the simple projective representations $\tilde P_{1,(j,k)}$ for $k\ne j$.
  Using the explicit description of $\tilde P_3^I$ from Example~\ref{ex:truncated lifts}, we see that each $\tilde P_{1,(j,k)}$ for $k\ne j$ is supported at a vertex which is not a neighbor of the support of $\tilde P_3^I$, which implies $\Ext\!\big(\tilde P_3^I,\tilde P_{1,(j,k)}\big)=0$ for $k\neq j$ and thus $\Ext\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$.

  If $m\geq 3$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m+1}^I,-)$ to the sequence
  \[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tau\tilde P_{m+1}^I}.\]
  Following Lemma~\ref{le:properties}.3, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$ and using the long exact sequence this immediately implies $\Hom\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.
  From Lemma~\ref{le:properties}.3 again, we have $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$.
  Using the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} and Lemma~\ref{le:properties}.4, we get
  \[\dim\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=1.\]
  It follows that the surjective map $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\to\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)$ appearing in the long exact sequence is in fact an isomorphism.
  But the Auslander-Reiten formulas and Lemma~\ref{le:properties}.4 again imply 
  \[\dim\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0.\]
  Combining with the preceding discussion, this gives $\Ext\!\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.
\qed\end{proof}

@@

Let $\eta:\ses{M}{B}{N}$ be a short exact sequence of $\widetilde{K(n)}$-representations.
For a fixed dimension vector $\tbfe$, there is an induced ``Caldero-Chapoton map'' between quiver Grassmannians
\begin{align*}
  \Psi=\Psi^\eta:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
  E&\mapsto \big(E\cap M,(E+M)/M\big).
\end{align*}
Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(F,G)\cong\mathbb{A}^{\dim\Hom(G,M/F)}$.
For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
\begin{equation}
  \label{eq:grassmannian decomposition}
  \Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.
\end{equation}
Then $\Psi$ restricts to a map
\[\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
The following results are proven in \cite[Section 3]{cefr}.
For completeness we include a proof of the first.
\begin{lemma}
  \label{le:good partition}
  There exists a total ordering $\preceq$ of the dimension vectors $\tbff$ appearing in the decomposition \eqref{eq:grassmannian decomposition} such that for any fixed $\tbff$ the subset 
  \[\bigsqcup_{ \tbff'\succeq\tbff} \cG_{\tbff',\tbfe-\tbff'}\]
  is closed in $\Gr_\tbfe(B)$.
\end{lemma}
\begin{proof}
  Recall that $\Gr_\tbfe(B)$ is a closed subvariety of $\prod_{i\in Q_0} \Gr_{e_i}(B_i)$.
  For each $i$, the inclusion $M_i\subset B_i$ induces an upper-semicontinuous function $\rho_i:\Gr_{e_i}(B_i)\to\ZZ$ given by $\rho_i(E_i)=\dim(E_i\cap M_i)$.
  In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(B_i)$.
  It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\prec\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
  \[\bigsqcup_{ \tbff'\succ\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(B)\]
  for any fixed $\tbff$.
  Any refinement of this partial order to a total order $\preceq$ will give the claim.
\qed\end{proof}
\begin{theorem}
  \label{vb}
  If $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_{\tbff,\tbfg}$ is constant over $\Im\big(\Psi_{\tbff,\tbfg}\big)$, then $\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to\Im\big(\Psi_{\tbff,\tbfg}\big)$ is an affine bundle.
  In particular, the existence of a cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}

\begin{remark}
  \label{rem:cell decompositions}
  To apply Theorem~\ref{vb} and establish cell decompositions for the $\cG_{\tbff,\tbfg}$, we will find a cell decomposition of $\Gr_\tbff(M)\times\Gr_\tbfg(N)$ such that $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is a union of affine cells, giving an induced cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$.

  By Lemma~\ref{le:good partition}, the existence of cell decompositions for each $\cG_{\tbff,\tbfg}$ implies the existence of a cell decomposition for $\Gr_\tbfe(B)$.
  Indeed, we may take the affine cells of all the $\cG_{\tbff,\tbfg}$ as affine cells of $\Gr_\tbfe(B)$ with the natural lexicographic total order induced by taking cells from $\cG_{\tbff',\tbfg'}$ after those of $\cG_{\tbff,\tbfg}$ whenever $\tbff'\succ\tbff$.
\end{remark}

>>>>

The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge2$, the following hold:
  \begin{enumerate}
    \item For $i\in\{1,\ldots,n\}$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$ and any $J\subsetneq\{i\}^c$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{
           \ar[r] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[d]
          & \ar[r] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[d] \ar_{\tilde\pi_{m,i}^{\{j\}^c}}[dl] 
          & \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[d] \ar_{\tilde\pi_{m+1}^{\{i\}^c}}[dl]\\ 
          \tilde P_{m-1,(i,j)}^{\{j\}}\cong \tilde P_{m,i}^{\{j\}^c}
          & \tilde P_{m,i}^{\{i\}}\cong\tilde P_{m+1}^{\{i\}^c} \ar_(.4){\tilde\pi_{m,i}^{\{j\}^c,\{i\}}}[l] 
          & \tilde P_{m+1}^J \ar_(.4){\tilde\pi_{m+1}^{\{i\}^c,J}}[l]}
      \end{equation}
    \item For an admissible sequence $\ui\in A_1^{(k)}$, $1\le k< m$, and $J\subsetneq\{1,\ldots,n\}$, the restriction of $\tilde\pi_{m+1}^J:\tilde P_{m+1}\to\tilde P_{m+1}^J$ to $\tilde P_{m+1-k,\ui}$ is injective if $J\subsetneq\{i_1\}^c$ and is zero if $i_1\in J$.
    \item For any admissible word $\ui\in A_1^{(k)}$ with $0\le k< m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with~$i_k\in I$ and $i_1\notin J$ if $k\ge1$ or with $J\subsetneq I$ if $k=0$, there exist (unique up to scale) surjective maps~$\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$.
      These satisfy the following relations:
      \begin{itemize}
        \item $\tilde\pi_{m+1}^{\ui,I,J}\circ\tilde\pi_{m+1}^{J,K}=\tilde\pi_{m+1}^{\ui,I,K}$ for $K\subsetneq J$;
          \item $\tilde\pi_{m+1-k,\ui}^{H,I}\circ\tilde\pi_{m+1}^{\ui,I,J}=\tilde\pi_{m+1}^{\ui,H,J}$ for $I\subsetneq H\subsetneq\{1,\ldots,n\}$;
        %\item $\tilde\pi_{m+1}^{\ui,\varnothing,I}\Big|_{\tilde P_{m+1-k,\ui}} =\tilde\pi_{m+1-k,\ui}^I$;
        \item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $1\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
      \end{itemize}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

@@

  The diagrams from (2) stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
  \[\tilde\pi_{m+1}^{\ui,I,J}:=\tilde\pi_{m+1-k,\ui}^{I,\{i_k\}}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_k\}^c,\{i_{k-1}\}}\circ\cdots\circ\tilde\pi_{m,i_1}^{\{i_2\}^c,\{i_1\}}\circ\tilde\pi_{m+1}^{\{i_1\}^c,J}.\]
  These can be seen to satisfy the desired properties from (4) inductively using Lemma~\ref{le:properties}.5 and the commutativity from (2).
\qed\end{proof}

The next technical results illustrate the need to lift to the universal covering quiver $\widetilde K(n)$.
\begin{lemma}
  \label{le:special subrepresentations}
  Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
  \begin{enumerate}
    \item For $m\ge2$, we have $\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)\cong\CC$.
      Moreover, the kernel of a nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is the following representation 
      \[\tilde P_m(j,I):=
        \begin{cases}
          \bigoplus_{\substack{1\leq k\leq n\\k\neq j}}\tilde P_{m-1,(j,k)}\oplus \bigoplus_{i\in I\setminus\{j\}}\tilde P_{m-2,(j,j,i)} & \text{ if $m\geq 3$;}\\
          \bigoplus_{\substack{1\leq k\leq n\\k\neq j}}\tilde P_{1,(j,k)} & \text{ if $m=2$.}
        \end{cases}\]
    \item For $m\ge3$, any nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is surjective.
  \end{enumerate}
\end{lemma}
\begin{proof}
  The first claim of part (1) follows immediately by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} to Lemma~\ref{le:properties}.3.
  Indeed, this gives
  \[\dim\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})=1.\]

@@

  Since the evaluation map $ev_I$ in equation~\eqref{ses1} is irreducible, any nontrivial map to $\tilde P_{m-1}^{I\setminus\{j\}}$ must factor through $\tilde P_{m-1}$.
  It then follows from Lemma~\ref{le:homdecomposition} that $\tilde P_{m-1,(j,k)}$ is in the kernel of the vertical morphism $\eta$ for $k\ne j$.
  Therefore $\ker\eta$ is the direct sum of these with the kernel of the induced map $\tilde P_{m-1}\to\tilde P_{m-1}^{I\setminus\{j\}}$, that is with $\bigoplus_{i\in I\setminus\{j\}} \tilde P_{m-2,i}=\bigoplus_{i\in I\setminus\{j\}} \tilde P_{m-2,(j,j,i)}$, and so $\ker\eta=\tilde P_m(j,I)$.
  Since $\eta$ and the right hand vertical morphism have the same kernel, this completes the proof of (1).

@@

The following orthogonality property is a primary reason we need to lift to the universal cover of $K(n)$.
As usual, given $\tilde M\in\rep \widetilde{K(n)}$, we write
\[\tilde M^\perp := \{\tilde N\in\rep \widetilde{K(n)}:\Hom(\tilde M,\tilde N)=0=\Ext(\tilde M,\tilde N)\}.\]
\begin{corollary}
  \label{cor:perpendicular}
  Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
  For $m\geq 2$, we have $\tilde P_m(j,I)\in (\tilde P_{m+1}^I)^\perp$.
\end{corollary}
\begin{proof}
  If $m=2$, we have $\Hom\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$ since $\tilde P_2(I,j)$ is a direct sum of the simple projective representations $\tilde P_{1,(j,k)}$ for $k\ne j$.
  Using the explicit description of $\tilde P_3^I$ from Example~\ref{ex:truncated lifts}, we see that each $\tilde P_{1,(j,k)}$ for $k\ne j$ is supported at a vertex which is not a neighbor of the support of $\tilde P_3^I$, which implies $\Ext\!\big(\tilde P_3^I,\tilde P_{1,(j,k)}\big)=0$ for $k\neq j$ and thus $\Ext\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$.

  If $m\geq 3$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m+1}^I,-)$ to the sequence
  \[\ses{\tilde P_m(j,I)}{\tilde P_{m,j}}{\tau\tilde P_{m+1}^I}.\]
  Following Lemma~\ref{le:properties}.3, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$ and using the long exact sequence this immediately implies $\Hom\big(\tilde P_{m+1}^I,\tilde P_m(j,I)\big)=0$.
  From Lemma~\ref{le:properties}.3 again, we have $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$.
  Using the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} and Lemma~\ref{le:properties}.4, we get
  \[\dim\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=1.\]
  It follows that the surjective map $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\to\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)$ appearing in the long exact sequence is in fact an isomorphism.
  But the Auslander-Reiten formulas and Lemma~\ref{le:properties}.4 again imply 
  \[\dim\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0.\]
  Combining with the preceding discussion, this gives $\Ext\!\big(\tilde P_{m+1}^I,\tilde P_m(j,I)\big)=0$.
\qed\end{proof}

@@

Let $\eta:\ses{\tilde M}{\tilde B}{\tilde N}$ be a short exact sequence of $\widetilde{K(n)}$-representations.
For a fixed dimension vector $\tbfe$, there is an induced ``Caldero-Chapoton map'' between quiver Grassmannians
\begin{align*}
  \Psi=\Psi^\eta:\Gr_\tbfe(\tilde B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(\tilde M)\times \Gr_\tbfg(\tilde N)\\
  E&\mapsto \big(\tilde E\cap \tilde M,(\tilde E+\tilde M)/\tilde M\big).
\end{align*}
Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(\tilde F,\tilde G)\cong\mathbb{A}^{\dim\Hom(\tilde G,\tilde M/\tilde F)}$.
For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(\tilde M)\times \Gr_\tbfg(\tilde N)\big)$, we have 
\begin{equation}
  \label{eq:grassmannian decomposition}
  \Gr_\tbfe(\tilde B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.
\end{equation}
Then $\Psi$ restricts to a map
\[\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(\tilde M)\times \Gr_\tbfg(\tilde N).\]
The following results are proven in \cite[Section 3]{cefr}.
For completeness we include a proof of the first.
\begin{lemma}
  \label{le:good partition}
  There exists a total ordering $\preceq$ of the dimension vectors $\tbff$ appearing in the decomposition \eqref{eq:grassmannian decomposition} such that for any fixed $\tbff$ the subset 
  \[\bigsqcup_{ \tbff'\succeq\tbff} \cG_{\tbff',\tbfe-\tbff'}\]
  is closed in $\Gr_\tbfe(\tilde B)$.
\end{lemma}
\begin{proof}
  Recall that $\Gr_\tbfe(\tilde B)$ is a closed subvariety of $\prod_{i\in Q_0} \Gr_{e_i}(\tilde B_i)$.
  For each $i$, the inclusion $\tilde M_i\subset \tilde B_i$ induces an upper-semicontinuous function $\rho_i:\Gr_{e_i}(B_i)\to\ZZ$ given by $\rho_i(\tilde E_i)=\dim(\tilde E_i\cap \tilde M_i)$.
  In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(\tilde B_i)$.
  It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\prec\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
  \[\bigsqcup_{ \tbff'\succ\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(\tilde B)\]
  for any fixed $\tbff$.
  Any refinement of this partial order to a total order $\preceq$ will give the claim.
\qed\end{proof}
\begin{theorem}
  \label{vb}
  If $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_{\tbff,\tbfg}$ is constant over $\Im\big(\Psi_{\tbff,\tbfg}\big)$, then $\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to\Im\big(\Psi_{\tbff,\tbfg}\big)$ is an affine bundle.
  In particular, the existence of a cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}

\begin{remark}
  \label{rem:cell decompositions}
  To apply Theorem~\ref{vb} and establish cell decompositions for the $\cG_{\tbff,\tbfg}$, we will find a cell decomposition of $\Gr_\tbff(\tilde M)\times\Gr_\tbfg(\tilde N)$ such that $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is a union of affine cells, giving an induced cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$.

  By Lemma~\ref{le:good partition}, the existence of cell decompositions for each $\cG_{\tbff,\tbfg}$ implies the existence of a cell decomposition for $\Gr_\tbfe(\tilde B)$.
  Indeed, we may take the affine cells of all the $\cG_{\tbff,\tbfg}$ as affine cells of $\Gr_\tbfe(\tilde B)$ with the natural lexicographic total order induced by taking cells from $\cG_{\tbff',\tbfg'}$ after those of $\cG_{\tbff,\tbfg}$ whenever $\tbff'\succ\tbff$.
\end{remark}
